Homework

### 2016-07-07 Macro Impacts Revised.tex
Shear

Observe the dispersion relation $\beta k=\omega$, which holds for each component $a_i$, and that $\beta=\f\mu\rho$. Thus, the solutions to the wave equation are

@@

Now we take the curl of $A$ to find the shear mode displacement

@@

U_x&=\f{k_z^2(k_x\Sigma_{yz}-k_z\Sigma_{xy})+k_y^2(k_x\Sigma_{yz}-k_y\Sigma_{zx})}{\mu k_y k_z k^2}\,,\\
U_y&=\f{k_x^2(k_y\Sigma_{zx}-k_x\Sigma_{yz})+k_z^2(k_y\Sigma_{zx}-k_z\Sigma_{xy})}{\mu k_z k_x k^2}\,,\\
U_z&=\f{k_y^2(k_z\Sigma_{xy}-k_y\Sigma_{zx})+k_x^2(k_z\Sigma_{xy}-k_x\Sigma_{yz})}{\mu k_x k_y k^2}\,,

@@

Assuming radial symmetry, we have $\Sigma=\Sigma_{zz}=-2\Sigma_{xx}=-2\Sigma_{yy}$.

The energy of these shear waves is given
\begin{align}
E&=\f12\int_V\p{\rho\abs{u_t}^2+\mu\abs{\nabla\cdot u}^2}\,,\\
&=\rho\int_V\abs{u_t}^2\,,\\
&=\mu\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
\end{align}
The integral is horribly divergent about the azimuth - there must have been a mistake...

>>>>

Observe the dispersion relation $\beta k=\omega$, which holds for each component $a_i$, and that $\beta^2=\f\mu\rho$. Thus, the solutions to the wave equation are

@@

Now we take the curl of $A$ to find the shear mode displacement and use the relations (73) through (75) to obtain

@@

U_x&=-\I\f{\Sigma_{xx}}{2k_x\mu}\,,\\
U_y&=-\I\f{\Sigma_{yy}}{2k_y\mu}\,,\\
U_z&=-\I\f{\Sigma_{zz}}{2k_z\mu}\,,

@@

The energy of these shear waves is given
E&=\f12\int_V\p{\rho\abs{u_t}^2+\mu\abs{\nabla\cdot u}^2}\,,\\
&=\rho\int_V\abs{u_t}^2\,,\\
&=\rho\beta^2\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{\f{\Sigma_{zz}^2\sec^2\theta+\csc^2\theta(\Sigma_{yy}^2\csc^2\phi+\Sigma_{xx}^2\sec^2\phi)}{4\mu^2}}\,,\\
Assuming axial symmetry, we have $\Sigma_{xx}=\Sigma\cos^2\theta$, $\Sigma_{yy}=\Sigma\sin^2\theta$, and $\Sigma_{zz}=-\Sigma$. Hence, 
E&=\mu\int\f{\diff^3 k}{(2\pi)^3}\Sigma^2\p{\f{\sec^2\theta+\csc^2\theta}{4\mu^2}}\,,\\
&=\f{1}{\mu}\int\f{\diff^3 k}{(2\pi)^3}\Sigma^2\csc^2(2\theta)\,,\\
&=\f{1}{\mu}\int\f{\diff k\diff\theta}{(2\pi)^2}\Sigma^2k^2\csc^2(2\theta)\,.
